\begin{frame}[allowframebreaks]{References}
  \begin{itemize}
    \item[{\bf [1]}] A. Butko, R. Garibotti, L. Ost, and G. Sassatelli, \textbf{\textit{“Accuracy evaluation of GEM5 simulator system,”}} in 7th International Workshop on Reconfigurable and Communication-Centric Systems-on-Chip (ReCoSoC), 2012.
    
    \item[{\bf [2]}] S. V. Bharadwaj and C. K. Vudadha, \textbf{\textit{“Evaluation of x86 and ARM architectures using compute-intensive workloads,”}} in 2022 IEEE International Symposium on Smart Electronic Systems (iSES), 2022.
    
    \item[{\bf [3]}] R. Saha, Y. P. Pundir, S. Yadav, and P. K. Pal, \textbf{\textit{“Impact of size, latency of cache-L1 and workload over system performance,”}} in 2020 International Conference on Advances in Computing, Communication Materials (ICACCM), 2020.
    
    \item[{\bf [4]}] A. D. George, \textbf{\textit{“An overview of RISC vs. CISC,”}} in Proceedings of the Twenty-Second Southeastern Symposium on System Theory, 1990.
    
    \item[{\bf [5]}] M. Ling, X. Xu, Y. Gu, and Z. Pan, \textbf{\textit{“Does the ISA really matter? A simulation-based investigation,”}} in 2019 IEEE Pacific Rim Conference on Communications, Computers and Signal Processing (PACRIM), 2019.
    
    \item[{\bf [6]}] T. Jamil, \textbf{\textit{“RISC versus CISC,”}} IEEE Potentials, vol. 14, no. 3, pp. 13–16, 1995.
    
    \item[{\bf [7]}] A. A. Abudaqa, T. M. Al-Kharoubi, M. F. Mudawar, and A. Kobilica, \textbf{\textit{“Simulation of ARM and x86 microprocessors using in-order and out-of-order CPU models with gem5 simulator,”}} in 2018 5th International Conference on Electrical and Electronic Engineering (ICEEE), pp. 317–322.
    
    \item[{\bf [8]}] B. Vikas and B. Talawar, \textbf{\textit{“On the cache behavior of Splash-2 benchmarks on ARM and Alpha processors in gem5 full system simulator,”}} in 2014 3rd International Conference on Eco-friendly Computing and Communication Systems, pp. 5–8.
    
    \item[{\bf [9]}] S. Lee, Y. Kim, D. Nam, and J. Kim, \textbf{\textit{“Gem5-AVX: Extension of the Gem5 Simulator to Support AVX Instruction Sets,”}} IEEE Access, 2024.
  \end{itemize}
\end{frame}
