The landscape of embedded systems development and research has been significantly shaped by the availability and capability of architectural simulators. Among these, the Gem5 simulator stands out as a powerful and flexible platform for computer architecture research. However, despite its extensive support for mainstream architectures like ARM, x86, and RISC-V, there remains a notable gap in its coverage of microcontroller architectures that are fundamental to embedded systems and IoT devices.

\subsection{Background and Motivation}

Microcontrollers, particularly those based on the AVR architecture, have been cornerstone components in embedded systems education and development for decades. The AVR architecture, known for its simplicity, efficiency, and widespread use in Arduino platforms, represents an ideal candidate for educational and research purposes. However, the current limitation of Gem5 in supporting such architectures creates a significant barrier in:
\begin{itemize}
    \item Academic research requiring detailed microcontroller simulation
    \item Educational environments teaching embedded systems concepts
    \item Development workflows requiring accurate performance analysis
    \item Comparative studies across different microcontroller architectures
\end{itemize}

\subsection{Project Objectives}
This project aims to bridge this critical gap by extending the Gem5 simulator to support the AVR architecture, complemented by a comprehensive GUI-based debugging and visualization system. The specific objectives include:
\begin{enumerate}
    \item Implementation of complete AVR instruction set support within Gem5
    \item Development of accurate timing and pipeline models
    \item Integration of peripheral functionality typical in microcontroller systems
    \item Creation of an intuitive GUI interface for simulation control and analysis
    \item Validation through comprehensive benchmarking and comparison studies
\end{enumerate}

\subsection{Scope and Significance}
The scope of this project encompasses:
\begin{itemize}
    \item Full implementation of the AVR instruction set architecture
    \item Accurate modeling of timing and pipeline behavior
    \item Development of peripheral models (UART, Timer, GPIO)
    \item Creation of a GUI-based debugging and visualization system
    \item Comprehensive validation and performance analysis framework
\end{itemize}

The significance of this work lies in its potential to:

\begin{itemize}
    \item Enable detailed microcontroller architecture research
    \item Provide educational tools for embedded systems teaching
    \item Facilitate comparative studies between different architectures
    \item Support embedded software development and optimization
\end{itemize}

\subsection{Technical Approach}

Our approach combines systematic architecture implementation with modern software engineering practices:
\begin{itemize}
    \item Modular development methodology
    \item Extensive testing and validation procedures
    \item Integration with existing Gem5 frameworks
    \item User-centric GUI design principles
\end{itemize}

\subsection{Report Organization}

The remainder of this report is organized as follows:

\textbf{Section 2} presents a comprehensive literature review and related work.

\textbf{Section 3} details the system architecture and design methodology.

\textbf{Section 4} describes the implementation details and technical challenges.

\textbf{Section 5} presents experimental results and performance analysis.

\textbf{Section 6} discusses the challenges encountered and solutions developed.

\textbf{Section 7} outlines future work and potential enhancements.

\textbf{Section 8} concludes with a summary of achievements and contributions.

This extension of the Gem5 simulator represents a significant step forward in microcontroller architecture simulation capabilities, providing researchers, educators, and developers with a powerful tool for understanding and optimizing embedded systems.